---
title: "A1-6-Build an interactive application for prediction"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Start with the iris dataset code examples.

Build a function that determines the distance for a new iris (specified by the four measurements), when compared to a cluster centre. Build another function that looks at all the cluster centres and tells you which cluster is the closest to the new iris. Use the dist function.

Then create an interactive application that takes values for the dimensions of both the Petal and Sepal of a newly measured Iris, and then classify it as one of the three species. The easiest way to do this is to use four sliders, with ranges pre-specified to the extents of the existing dataset. The application could just state the species that it thinks is correct. 

```{r}
# Write your code and your comments here.
# Import library
library(ggplot2)
library(shiny)
library(class)

set.seed(101)
irisCluster <- kmeans(iris[,1:4], center=3, nstart=20)
saveRDS(irisCluster, "irisCluster.rds")

ui<- fluidPage(
titlePanel(title=" Iris Prediction "),
sidebarLayout(
sidebarPanel(
  sliderInput('sLength', 'Sepal.Length', min=4, max=8, value=4, step=0.1, round=0),
  sliderInput('sWidth', 'Sepal.Width', min=2, max=4.5, value=2, step=0.1, round=0),
  sliderInput('pLength', 'Petal.Length', min=1, max=7, value=1, step=0.1, round=0),
  sliderInput('pWidth', 'Petal.Width', min=0, max=2.5, value=0, step=0.1, round=0)
),
mainPanel(
  h3(textOutput('title')),
  verbatimTextOutput('result')
))
)

server<- function (input, output){
  data <- reactive({
    data.frame(Sepal.Length=input$sLength,
               Sepal.Width=input$sWidth,
               Petal.Length=input$pLength,
               Petal.Width=input$pWidth)
  })
  
  closest.cluster <- function(x) {
    cluster.dist <- apply(irisCluster$centers, 1, function(y) sqrt(sum((x-y)^2)))
    return(which.min(cluster.dist)[1])
  }
  cluster <- reactive({
    apply(data(), 1, closest.cluster)
  })
  
  species <- c("setosa", "versicolor", "virginica")
  
  t <- "The specie for the features you selected is:"
  
  output$title <- renderText(t)

  output$result <- renderText(species[cluster()])
}

shinyApp (ui = ui , server = server )


# Any plot you generate will be shown in the document.
```
