---
title: "Assessment 2"
author: "14088355 Yiyan Gao"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## New York Air Quality Measurements Exploratory Data Analysis and Linear Regression Model

```{r}
library(dplyr)
library(gridExtra)
library(ROCR)
library(tidyverse)
library(caret)
library(moments)
```
1. Check the first rows of the dataset

1.1 Load data
```{r}
data(airquality)
```

1.2 Check the dimension of the dataset
```{r}
dim(airquality)
```

1.3 Show first few rows of the dataset
```{r}
head(airquality)
```

1.4 Check the type of the data in each column
```{r}
sapply(airquality, class)
```

2. Missing value handling and data cleaning

2.1 Check if the data is clean, that means it is not missing any values

2.1.1 Check duplicated rows
```{r}
sum(duplicated(airquality))
```

2.1.2 Check values that are na
```{r}
sum(!complete.cases(airquality))
```

2.1.3 Check the numnber of na values in each column
```{r}
sapply(airquality, function(x) sum(is.na(x)))
```

2.2 Remove rows with missing values
```{r}
df <- na.omit(airquality)
```

Show that there is no null values
```{r}
sum(!complete.cases(df))
```

2.3 Change Month and Day to factor variables
```{r}
df$Month <- factor(df$Month, levels=5:9, labels=month.abb[5:9], ordered=TRUE)
df$Day <- factor(df$Day, levels=c(1:31), ordered=TRUE)
```

3. Explorative Data Analysis

3.1 Describe the dataset

3.1.1 Dimension of the dataset
```{r}
dim(df)
```

3.1.2 Summary of the dataset
```{r}
summary(df)
```

3.2 Distribution of Ozone

3.2.1 Histogram of Ozone
```{r}
ggplot(data=df, aes(x=Ozone)) +
  geom_histogram(fill="steelblue", color="black") +
  ggtitle("Histogram of Ozone")
```

3.2.2 Check the skewness
```{r}
skewness(df$Ozone, na.rm = T)
```

3.2.3 Check the kurtosis
```{r}
kurtosis(df$Ozone, na.rm=T)
```

3.24 Scale Ozone for more symmetric distribution
```{r}
df$Ozone.S <- sqrt(df$Ozone)
ggplot(data=df, aes(x=Ozone.S)) +
  geom_histogram(fill="steelblue", color="black") +
  ggtitle("Histogram of Ozone.S")
```

3.3 Plot each attribute against Ozone
```{r}
p1 <- ggplot(df, aes(x=Solar.R, y=Ozone.S)) + geom_point()
p2 <- ggplot(df, aes(x=Wind, y=Ozone.S)) + geom_point()
p3 <- ggplot(df, aes(x=Temp, y=Ozone.S)) + geom_point()
p4 <- ggplot(df, aes(x=Month, y=Ozone.S)) + geom_boxplot()
p5 <- ggplot(df, aes(x=Day, y=Ozone.S)) + geom_boxplot()
grid.arrange(p1, p2, p3, p4, p5, nrow = 3)
```

3.4 Pair plot for all numeric variables
```{r}
pairs(df, panel = panel.smooth, main = "airquality data")
```

3.5 Check the correlations between variables
```{r}
# Choose the numerical columns
columns <- c('Ozone.S', 'Solar.R', 'Wind', 'Temp')
round(cor(df[, columns]), 2)
```

Ozone is moderately correlated with Solar.R, strongly correlated with Wind,
strongly correlated to Temperature.
Solar.R is weakly correlated with Wind and Temp.
Wind is moderately correlated to Temp.

4. Train a linear regression model and evaluate the model

4.1 Train the model
```{r}
set.seed(0)
training.samples <- df$Ozone.S %>%
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- df[training.samples, ]
test.data <- df[-training.samples, ]

model <- lm(Ozone.S ~., data = train.data)
summary(model)
saveRDS(model, "model.rds")
```

4.2 Evaluation of th model
```{r}
predictions <- model %>% predict(test.data)
RMSE(predictions, test.data$Ozone.S)
R2(predictions, test.data$Ozone.S)
```

5. Develop a Shiny application to predict the Ozone level
```{r}
library(shiny)
ui<- fluidPage(
titlePanel(title=" Air Quality Prediction "),
sidebarLayout(
sidebarPanel(
  sliderInput('solar', 'Solar Radiation', min=7, max=334, value=7, step=1, round=0),
  sliderInput('wind', 'Wind', min=2, max=21, value=2, step=1, round=0),
  sliderInput('temp', 'Temperature', min=55, max=100, value=55, step=1, round=0),
  selectInput('month', 'Month', c('May', 'Jun', 'Jul', 'Aug', 'Sep')),
  selectInput('day', 'Day', c(1:31)),
),
mainPanel(
  h3(textOutput('title')),
  verbatimTextOutput('result')
))
)

server<- function (input, output){
  data <- reactive({
    data.frame(Solar.R=input$solar,
               Wind=input$wind,
               Temp=input$temp,
               Month=input$month,
               Day=input$day,
               Ozone=0
               )
  })
  
  prediction <- reactive({
    predict(model, newdata = data())
  })
  
  t <- "Predicted Air Quality - Square Root of Ozone Level:"
  
  output$title <- renderText(t)

  output$result <- renderText(prediction())
}

shinyApp (ui = ui , server = server )
```


